Case based Arabic Morphological Analysis with Compositional Non-deterministic Automata

### 2010-06-25 trunk/tex/sarf.tex
added the example diagram and 2 sentences which are not yet proofread and working on to explain it in detail

>>>>

\usepackage{relsize}
\usepackage{fancyvrb}
%\usepackage{times}
\usepackage{latexsym}

The hadith case study is interesting for Sarf since the controller
considers most of the analyses where we have a concentration
of proper names in the text, and ignores most of the analyses as long 
as they are valid where we do not have proper names. 
The controller is also interested in a small subset of words 
that relate persons to each other such as \RL{bin} or ``the sun of''
or words that mean narrate such as \RL{qaal} or ``said''. 
With Sarf, we successfully automated the analysis of 
three books of Islamic narrations~\cite{narrations1,narrations2, narrations3}
and extracted from each one of them a vector of a three level deep
complex structure.

Many morphological analyzers exist~\cite{Sughaiyer:04}. 
Some use specialized part of speech tag sets~\cite{Khoja:01,Darwish:02}.

Buckwalter: used lexicon, added proper nouns, word based, recursive affixes

MAGEAD

Beeseley: many compiled FSAs compared to compositions of three FSAs

SAMA: word based, treebank specific,

MADA+TOKAN: no controller, we do not need a tokenizer

AMIRA: machine learning...

ElixirFM:

\subsection{Motivating Example}
% the FSMs for the three words
To help illustrate the strength of the method we imploy, we clarify it by walking through an example explaining the stages that lead to morphological analysis in SARF. Figure \ref{f:examples} shows a partial snapshot of the FSM's needed to analyze the following words: \RL{wsyal`bhaa}, \RL{syalbisohomaa} and \RL{al-laa`bown}.

\subsection{Non-deterministic Composition of FSMs}
% algorithm
% diagram of abstract machines
\begin{figure*}[tb]
\center{
\resizebox{1.8\columnwidth}{!}
{ \input{psfigs/abstract_machine.pstex_t}}
\caption{Abstract FSM.}
\label{f:abstract}
}
\end{figure*}

\end{document}
=======
%
% File naaclhlt2010.tex
%
% Contact: nasmith@cs.cmu.edu
